ODGI: scalable tools for pangenome graphs

### 2021-06-04 manuscript/main.tex
complete affiliation of SH

    \title[ODGI: scalable tools for pangenome graphs]{ODGI: scalable tools for pangenome graphs}
    \author[Guarracino, Heumos \textit{et~al}.]{
        Andrea Guarracino\,$^{\text{\sfb 1,}*}$,
        Simon Heumos\,$^{\text{\sfb 2,}*}$,
    % XXXXX,
        Pjotr~Prins\,$^{\text{\sfb 3}}$ and
        Erik~Garrison\,$^{\text{\sfb 3,}\dagger}$
        \footnote{The authors wish it to be known that the first two authors should be regarded as joint first authors.}
    }
    \address{$^{\text{\sf 1}}$Biology, University of Tor Vergata, Rome, 00133, Italy \\
        $^{\text{\sf 2}}$QBiC, University of Tübingen, Tübingen, XXXXXXXXXX, Germany \\
        $^{\text{\sf 3}}$Dept. Genetics Genomics \& Informatics, UTHSC, Memphis, TN, USA
    }

>>>>

    \title[ODGI: scalable tools for pangenome graphs]{ODGI: scalable tools for pangenome graphs}
    \author[Guarracino, Heumos \textit{et~al}.]{
        Andrea Guarracino\,$^{\text{\sfb 1,}*}$,
        Simon Heumos\,$^{\text{\sfb 2,}*}$,
    % XXXXX,
        Pjotr~Prins\,$^{\text{\sfb 3}}$ and
        Erik~Garrison\,$^{\text{\sfb 3,}\dagger}$
        \footnote{The authors wish it to be known that the first two authors should be regarded as joint first authors.}
    }
    \address{$^{\text{\sf 1}}$Biology, University of Tor Vergata, Rome, 00133, Italy \\
        $^{\text{\sf 2}}$Quantitative Biology Center (QBiC), University of Tübingen, Tübingen, 72076, Germany \\
        $^{\text{\sf 3}}$Dept. Genetics Genomics \& Informatics, UTHSC, Memphis, TN, USA
    }
